### 2024-10-29 paper/3-motivation.tex
Minor fix

\begin{align}
  &c^* \vdash call(\$push42), ~ f32.const ~ 3.14 \label{eq:call-1} \\
&\leadsto
  Label(\epsilon), ~ Frame(), ~ c^* \vdash i32.const ~ 42, ~ end, ~ f32.const ~ 3.14 \label{eq:call-2} \\
&\leadsto
  Label(\epsilon), ~ Frame(), ~ c^* \vdash end, ~ f32.const ~ 3.14 \label{eq:call-3} \\
&\leadsto
  c^* \vdash f32.const ~ 3.14 \label{eq:call-4} \\
&\leadsto
  c^* \label{eq:call-5}
\end{align}

>>>>

\begin{align}
  &c^* \vdash call(\$push42), ~ f32.const ~ 3.14 \label{eq:call-1} \\
&\leadsto
  Label(\epsilon), ~ Frame, ~ c^* \vdash i32.const ~ 42, ~ end, ~ f32.const ~ 3.14 \label{eq:call-2} \\
&\leadsto
  Label(\epsilon), ~ Frame, ~ c^* \vdash end, ~ f32.const ~ 3.14 \label{eq:call-3} \\
&\leadsto
  c^* \vdash f32.const ~ 3.14 \label{eq:call-4} \\
&\leadsto
  c^* \vdash \epsilon \label{eq:call-5}
\end{align}
